---
title: "Step-by-Step GLM"
author: "Nathanael Bowles"
date: "February 3, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First I will take a look at how the data looks before we do anything. Here we simply have a histogram of the 

```{r}
library(ggplot2);

testdf <- xml_to_coordinates("~/LabWorkNathan/Data_for_Analysis/all_xml_files/X400x426L-2m2.xml")

  ggplot(data = testdf, aes(x=type)) +
      geom_bar()  +
      ggtitle("X400x426L-2m2") +
      theme(plot.title = element_text(hjust = 0.5))
```

Next we want to view it in bins. We want at least 15 degrees of freedom. As such, we will mark xmax = kernel with largest x, then ((xmax-xmin)/16) will give us the bins we need.

```{r}
   #calculate amount of length per bin
   num_bins = 20

   xmax = max(testdf$x)
   xmin = min(testdf$x)
   bins = (xmax-xmin)/num_bins
   
   copy_df <- testdf
   
   
   #removes data frame names that would cause issues with the code
   rm(final_df)
   rm(GFP_df)
   rm(WT_df)
```

```{r}
   #split data into bins by brute force

   #make new data frame for being counted in next section
   final_df = data.frame(bins= seq(xmin,xmax,bins))
   WT_df = data.frame(WT = c(1:(nrow(final_df)))*0)
   GFP_df = data.frame(GFP = c(1:(nrow(final_df)))*0)
   
   
   #merge function adds an extra column called "Row.names" so I remove them immedietely after... twice
   final_df = merge(final_df, WT_df, by="row.names", sort=FALSE)
      final_df = subset(final_df, select = -c(Row.names))
   final_df = merge(final_df, GFP_df,by="row.names", sort=FALSE)
      final_df = subset(final_df, select = -c(Row.names))
  
   #sequences for the for-loops that come next
   sequence = seq(1,nrow(testdf)) 
   sequence2 = seq(1,nrow(final_df)-1)
```


```{r}

   #The brute force part, requires that the final_df is empty or it will double count

     for (val in sequence) {                                             #for each value
        for(i in sequence2) {                                              #for each bin
          
          #if the value is in the bin, but not any bins before it
          if ((copy_df$x[val] >= final_df$bins[i]) && (copy_df$x[val] < final_df$bins[i+1]) ) { 
            if (copy_df$type[val] == "WT") {                            #has to check if the kernel is WT or GFP then increments bin
               final_df$WT[i] = final_df$WT[i] + 1                      
            }               
            else if (copy_df$type[val] == "GFP") {
               final_df$GFP[i] = final_df$GFP[i] + 1
            }
          }
    
        }
     }

     #remove excess row
     final_df = final_df[-c(num_bins+1),]

  
```




```{r}
 #ggplot of the WT with respect to x
 ggplot(data = final_df, aes(x = bins, y = WT)) +
      geom_col()  +
      ggtitle("X400x426L-2m2") +
      ylim(0,15) +
      theme(plot.title = element_text(hjust = 0.5))

```




```{r}

 #ggplot of the GFP with respect to y
 ggplot(data = final_df, aes(x = bins, y = GFP)) +
      geom_col()  +
      ggtitle("X400x426L-2m2") +
      ylim(0,15) +
      theme(plot.title = element_text(hjust = 0.5))
```


Time to shove it into a GLM before the meeting
- logit link function
- quasi binomial function
- over dispersion is taken care of by logit link
- linear predictor

```{r}
glm(WT ~ bins,family = quasibinomial(link = "logit"), data = final_df)


```


