---
title: "Step-by-Step GLM"
author: "Nathanael Bowles"
date: "February 3, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First I will take a look at how the data looks before we do anything. Here we simply have a histogram of the 

```{r}
library(ggplot2);

#testdf <- xml_to_coordinates("~/LabWorkNathan/Data_for_Analysis/all_xml_files/X400x426L-2m2.xml")
testdf <- xml_to_coordinates(list[22])

  ggplot(data = testdf, aes(x=type)) +
      geom_bar()  +
      ggtitle("X400x426L-2m2") +
      theme(plot.title = element_text(hjust = 0.5))
```

Next we want to view it in bins. We want at least 15 degrees of freedom. As such, we will mark xmax = kernel with largest x, then ((xmax-xmin)/16) will give us the bins we need.

```{r}
   #calculate amount of length per bin
   num_bins = 30

   xmax = max(testdf$x)
   xmin = min(testdf$x)
   bins = (xmax-xmin)/num_bins
   
   copy_df <- testdf
   
   
   #removes data frame names that would cause issues with the code
   rm(final_df)
```

```{r}
   #split data into bins by brute 

   #make new data frame for being counted in next section
   final_df = data.frame(bins= seq(xmin,xmax,bins),WT = c(1:(num_bins+1))*0,GFP = c(1:(num_bins+1))*0)
  
  
   #sequences for the for-loops that come next
   sequence = seq(1,nrow(testdf)) 
   sequence2 = seq(1,nrow(final_df)-1)
```


```{r}

   #The brute force part, requires that the final_df is empty or it will double count

     for (val in sequence) {                                             #for each value
        for(i in sequence2) {                                              #for each bin
          
          #if the value is in the bin, but not any bins before it
          if ((copy_df$x[val] >= final_df$bins[i]) && (copy_df$x[val] < final_df$bins[i+1]) ) { 
            if (copy_df$type[val] == "WT") {                            #has to check if the kernel is WT or GFP then increments bin
               final_df$WT[i] = final_df$WT[i] + 1                      
            }               
            else if (copy_df$type[val] == "GFP") {
               final_df$GFP[i] = final_df$GFP[i] + 1
            }
          }
    
        }
     }

     #remove excess row
     final_df = final_df[-c(num_bins+1),]

  
```




```{r}
 #ggplot of the WT with respect to x
 ggplot(data = final_df, aes(x = bins, y = WT)) +
      geom_col()  +
      ggtitle("X400x426L-2m2") +
      ylim(0,15) +
      theme(plot.title = element_text(hjust = 0.5))

```




```{r}

 #ggplot of the GFP with respect to x
 ggplot(data = final_df, aes(x = bins, y = GFP)) +
      geom_col()  +
      ggtitle("X400x426L-2m2") +
      ylim(0,15) +
      theme(plot.title = element_text(hjust = 0.5))
```

Need to alter data into proportions rather than just # of kernels per bin for the logit link function.


This first attempt changes the values in final_df to (# of WT)/(# of kernels). This is an alternative to using the cbind() function to have it calculate successes vs failures. 

This method is definitely not correct. 

```{r}

sequence2 = seq(1, num_bins)
Total = final_df$WT + final_df$GFP

for (i in sequence2) {
  final_df$WT[i] = ((WT[i])/(Total[i]))
  final_df$GFP[i]= ((GFP[i])/(Total[i]))
}

```



Time to shove it into a GLM before the meeting
- logit link function
- quasi binomial function
- over dispersion is taken care of by logit link
- linear predictor

```{r}
transmission_rates = seq(1,30)
sequence = seq(1, nrow(final_df))

for (i in sequence) {
  transmission_rates[i] = final_df$GFP[i]/(final_df$WT[i] + final_df$GFP[i])
}

```

```{r}

GLM_combined_male = glm(cbind(GFP,WT) ~ bins,family = quasibinomial(link = "logit"), data = single_bin)

models1 = summary(GLM_combined_male)

models1

```

```{r}

model2 = glm(cbind(GFP,WT) ~ bins,family = quasibinomial(link = "logit"), data = final_df)

models2 = summary(model)

models2
```



