---
title: "TestingMendel"
author: "Nathanael Bowles"
date: "March 9, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("onewaytests")
library("ggplot2")
```

** We want to be able to compare each ear to a 50/50 coin flip 

load the files and fixes them so only working xml are included
```{r}
filenames = list.files("../Data_for_Analysis/curated_female_xml", pattern="*.xml", full.names=TRUE)

coords = lapply(filenames, xml_to_coordinates)

sequence = rev(seq(length(coords)))

for (i in sequence) {
  if (nrow(coords[[i]]) == 0)  {
    filenames = filenames[-i]
  }
}

coords = lapply(filenames, xml_to_coordinates)
```


Binomial test
```{r}

sequence = seq(1, length(coords))
results = seq(1, length(coords))

for (i in sequence) {
  test = xml_to_coordinates(filenames[i])
  total = nrow(test)
  test_bin = coordinates_to_xbins(test,30)
  succ = sum(test_bin$GFP)
  
  btest = binom.test(succ, total, p = .5, alternative = "two.sided")
  
  results[i] = btest$p.value
}


```

multiple test adjustment. Not needed for the next test since the goal of this test is to find "more normal" female ears. 
```{r}

##results = p.adjust(results, method = "bonferroni")

```


finishes setting up and plots a histogram of p-values.
```{r}

dfresults = data.frame(results)

dfresults <- data.frame(matrix(unlist(results), nrow=length(filenames), byrow=T),stringsAsFactors=FALSE)
names(dfresults)[names(dfresults) == colnames(dfresults[1])] = "p.value"

ggplot(data = dfresults, aes(p.value)) +
      geom_histogram(binwidth = .05) +
      xlab("p-value") +
      ylab("Per Ear Count") +
      ggtitle("Female P-value After Binomial Test and Adjustment") 

```


Removes from 'filenames' all female mutant parent ears with less than a .5 p-value.
```{r}
sequence = rev(seq(1, length(results)))

for (i in sequence) {
  if (results[i] < .5) {
    filenames = filenames[-i]
  }
}

```


Small notes:

- Only a 3-ish p-values are within a .05 threshold. However, these are ones REALLY close to 0 as they are ears with 3/270 GFP kernels. Now let's begin setting up a set of xml with .5 > P-value to use as a "baseline" for the assessing the distribution of the males. 
- For this I will use the Brown-Forsythe test because it is resistant to non-normal distributions (since we are assuming a quasi-binomial distributionw)

 
First we setup the female parents mutant allele ears based on what we found from the binomial test.
```{r}

#filenames = list.files("../Data_for_Analysis/curated_female_xml", pattern="*.xml", full.names=TRUE)

female_coords = lapply(filenames, xml_to_coordinates)

sequence = rev(seq(1, length(female_coords)))


for (i in sequence) {
  if (nrow(female_coords[[i]]) == 0)  {
    filenames = filenames[-i]
  }
}

female_coords = lapply(filenames, xml_to_coordinates)

female_bin_data = lapply(female_coords, function(x) {coordinates_to_xbins(x,30)})

```

```{r}
sequence = seq(length(male_bin_data)+1, length(female_bin_data) + length(male_bin_data)+1)

k=0

for (i in sequence) {
  k = k + 1
  GFP_l[i] = sum(male_bin_data[[k]]$GFP)
  WT_l[i] = sum(male_bin_data[[k]]$WT)
  mutant.allele.parent[i] = "Female"
}

sequence = seq(1, length(female_bin_data) + length(male_bin_data)+1)

for (i in sequence) {
  transmission_rate[i] = GFP_l[i]/(WT_l[i] + GFP_l[i])
}


```

Then we setup the male mutant allele ears.
```{r}

filenames = list.files("../Data_for_Analysis/curated_male_xml", pattern="*.xml", full.names=TRUE)

male_coords = lapply(filenames, xml_to_coordinates)

sequence = rev(seq(1, length(male_coords)))

for (i in sequence) {
  if (nrow(male_coords[[i]]) == 0)  {
    filenames = filenames[-i]
  }
}

male_coords = lapply(filenames, xml_to_coordinates)

male_bin_data = lapply(male_coords, function(x) {coordinates_to_xbins(x,30)})

```


```{r}
sequence = seq(1,length(male_bin_data))
GFP_l = sequence
WT_l = sequence
mutant.allele.parent = sequence

for (i in sequence) {
  GFP_l[i] = sum(male_bin_data[[i]]$GFP)
  WT_l[i] = sum(male_bin_data[[i]]$WT)
  mutant.allele.parent[i] = "Male"
}

```


combine into one data frame
```{r}

BF_DF = data.frame(transmission_rate, GFP_l, WT_l, mutant.allele.parent)

```

```{r}

results = bf.test(transmission_rate  ~ mutant.allele.parent, data = BF_DF, alpha = .05)

```



